Are mental properties supervenient on brain properties?

### 2011-08-05 nature_sci_rep/submission2/supervenience.tex
finished cep redline corrections

\newtheorem{defi}{Definition}
\newtheorem{thm}{Theorem}
\newtheorem{thex}{\emph{Gedankenexperiment}}
\lhead{Vogelstein JT, et al}
\rhead{Statistical Supervenience}

@@

\noindent The mind-brain supervenience notion was canonized in 1970 with the following quote from Donald Davidson \cite{Davidson70}:
\begin{quotation}
\noindent [mind-brain] supervenience might be taken to mean that there cannot be two events alike in all physical respects but differing in some mental respect, or that an object cannot alter in some mental respect without altering in some physical respect.
\end{quotation}
We consider a special case of supervenience of considerable interest.  Specifically, this work addresses a version of a local supervenience between mental properties and brain properties, with particular emphasize on brain-graphs (i.e., connectivity structure).  The determination of supervenience (or lack thereof) of a mental property on a brain property has potentially important implications in a number of fields of inquiry.  Neural network theory and artificial intelligence often implicitly take a generalized notion of local mind-brain supervenience as an assumption, which if falsified, might change modern approaches to learning \cite{Haykin2008,Ripley2008}. Cognitive neuroscience similarly seems to operate under such assumptions, which if falsified, might result in novel perspectives and theories \cite{Fodor1998, Gazzaniga2008}.  And the question of mind-brain supervenience continues to be debated amongst philosophers \cite{Kim2007}.

This work does not attempt to resolve any particular mind-brain supervenience debates.  Rather, we propose a statistical approach for framing mind-brain supervenience questions.  This approach depends on defining the space of mental and brain properties under investigation and a statistical model characterizing the possible distributions governing their relationship.  Such definitions transform supervenience from a conjecture or an assumption into a hypothesis which can be tested.

@@

\noindent Let $\mc{M}=\{m_1, m_2, \ldots\}$ be the space of all possible mental properties, including all possible thoughts, memories beliefs, etc.
Similarly, let $\mc{B}=\{b_1,b_2,\ldots\}$ be the set of all possible brain properties,
including the position and momentum of all subatomic particles within the skull.  
Given these definitions, Davidson's conjecture may be concisely and formally stated thusly:  $m \neq m' \implies b \neq b'$, where $(m,b), (m',b') \in \mc{M} \times \mc{B}$ are mind-brain pairs.  This mind-brain supervenience relation does not imply an injective relation, a causal relation, or an identity relation (see Appendix 1 for more details and some examples).  To facilitate both statistical analysis and empirical investigation, we convert this supervenience relation from a logical to a probabilistic relation.

% Let $b$ correspond to an agent's brain, which is a particular element from the set of all possible brains, $\mB$. Similarly, let $m$ correspond to an agent's mind, which is a particular element from the set of all possible minds, $\mM$.  
Let $F_{MB}$ indicate a joint distribution of minds and brains. Statistical supervenience can then be defined as follows:
\begin{defi}
\label{def1} 
$\mM$ is said to \textit{statistically supervene} on $\mB$ for distribution $F=F_{MB}$, denoted $\mM \overset{S}{\sim}_F \mB$, if and only if $\PP[m \neq m' | b=b']=0$, or equivalently $\PP[m = m' | b = b']=1$. 
\end{defi}
\noindent Statistical supervenience is therefore a probabilistic relation on sets (which could be considered a generalization of correlation; see Appendix 1 for details).

@@

Given that minds statistically supervene on brains, $\MsB$, then if two minds differ, there must be some brain-based difference to account for the mental difference.  This means that there must exist a deterministic function mapping each brain to its supervening mind, $g^*$. One could therefore, in principle, know this function. When the space of all possible minds is finite; that is, $|\mM| < \infty$, any function $g\from \mB \to \mM$ mapping from minds to brains is called a \emph{classifier}.  
% Let $\mh{m}$ denote the output of a classifier, $g(b)=\mh{m}$.  
Define misclassification rate, the probability that $g$ misclassifies $b$ under distribution $F=F_{MB}$,  as
\begin{align}
L_{F}(g) = \PP[g(B) \neq M] =  \sum_{(m,b) \in \mc{M} \times \mc{B}} \II\{g(b) \neq m\} \PP[B=b, M=m]	
\end{align}
where $\II$ denotes the indicator function taking value unity whenever its argument is true, and zero otherwise.  The Bayes optimal classifier $g^*$ minimizes $L_{F}(g)$ over all classifiers, that is:	
$g^* = \argmin_{g} L_{F}(g)$.
The \emph{Bayes error}, or Bayes risk, $L^*=L_{F}(g^*)$, is the minimum possible misclassification rate.

% The optimal such classifier, $g^*$, has the smallest expected misclassification rate, $L^*=L_{F}(g^*)$, under distribuion $F$.  The minimum misclassification rate is called Bayes error (see Methods for details). 
The primary result of casting supervenience in a statistical framework is the following theorem that we state without proof: 
\begin{thm}
\label{thm1} 
$\mM$ is said to \textit{statistically supervene} on $\mB$ for distribution $F=F_{MB}$, denoted $\mM \overset{S}{\sim}_{F} \mB$, if and only if $L^*= 0$. %Formally, \mbox{$\MsB \Leftrightarrow L^*=0$}.  
\end{thm}
% \begin{proof}
% Let $\mc{M}_b=\{m: \PP[B=b | M=m] >0\}$.  
% $$L^*=0 \Leftrightarrow |\mc{M}_b|=1 \, \forall \, b\in \mc{B} : \PP[B=b]>0. $$
% In words, for $L^*$ to equal 0, it must be the case that there exists only a single $m$ for each $b$.
% \end{proof}

@@

The above argument shows (for the first time to our knowledge) that statistical supervenience and zero Bayes error are equivalent. Statistical supervenience can therefore be thought of as a constraint on the possible distributions on minds and brains.  Specifically, let $\mc{F}$ indicate the set of all possible joint distributions on minds and brains, and let $\mc{F}_s = \{F_{MB} \in \mc{F}: L^*=0\}$ be subset of distributions for which supervenience holds. Theorem \ref{thm1} implies that $\mc{F}_s  \subsetneqq \mc{F}$.

\subsection*{The existence of a consistent statistical test for supervenience} % (fold)
\label{sub:subsection_name}

@@

The above theorem implies that if we desire to know whether a particular mental property is supervenient on a particular brain property, we must check whether $L^*=0$.  Unfortunately, $L^*$ is typically unknown.  Fortunately, we can approximate $L^*$ using training data.

Assume that training data $\mc{T}_n=\{(M_{1},B_{1}), \ldots, (M_{n},B_{n})\}$ are each sampled identically and independently (iid) from the true (but unknown) joint distribution, $F_{MB}$.  Let $g_n$ be a classifier induced by the training data, $g_n:\mB \times (\mc{M} \times \mc{B})^n \mapsto \mM$.  The expected misclassification rate of such a classifier is given by:
\begin{align}
\EE[L_F(g_n)]=\sum_{(m,b)  \in \mc{M}\times \mc{B}} \II\{g_n(b; \mc{T}_n) \neq m\} \PP[B=b,M=m],
\end{align}
%  The expected misclassification rate is given by 
% \begin{align}
% \EE[L_F(g_n)]=\sum_{(m,b)  \in \mc{M}\times \mc{B}} \II\{g_n(b; \mc{T}_n) \neq m\} \PP[B=b,M=m],
% \end{align}
where the expectation is taken with respect to the training data $\mc{T}_n$. Calculating the expected misclassification rate is often intractable in practice because it requires a sum over all possible mind-brain property pairs.  Instead, expected misclassification rate is approximated by ``hold-out'' error.  Let $\mc{H}_{n'}=\{(M_{n+1},B_{n+1}), \ldots, (M_{n+n'},B_{n+n'})\}$ be a set of $n'$ hold-out samples, each sampled iid from $F_{MB}$.  The hold-out approximation to misclassification rate is given by:
\begin{align}
\EE[L_F(g_n)] \approx \hL^{n'}_{F}(g_{n}) = \sum_{(M_i,B_i) \in \mc{H}_{n'}}\II \{g_{n}(B_i; \mc{T}_{n})\neq M_i\}, % \PP[B=b,M=m].	
\end{align}
% Under the above assumptions, $\hL^{n'}_F(g_n)$ 
which can be used as a surrogate for $L^*$. 
By definition of $g^*$, the expectation of $\hL^{n'}_F(g_n)$ (with respect to both $\mc{T}_n$ and $\mc{H}_{n'}$)  is greater than or equal to $g^*$ for any $g_n$ and all $n$.  Thus, we can construct a hypothesis test for $L^*$ using the surrogate $\hL^{n'}_F(g_n)$.

A statistical test proceeds by calculating a test statistic and a critical value $c_\alpha$.  We reject if the test statistic is more extreme than the critical value, or equivalently, if the $p$-value is less than $\alpha$, the allowable Type I error rate.   The $p$-value, the probability of rejecting the least favorable true null hypothesis (the hypothesis within the potentially composite null closest to the boundary with the alternate hypothesis), is a functional of the distribution of the test statistic.

Ideally, we might consider the following hypothesis test: $H_0: L^*>0$ and $H_A: L^*=0$.  Unfortunately, because the null hypothesis is not closed, the alternate hypothesis lies on the boundary, so the $p$-value is always equal to unity \cite{Bickel2000}.  To proceed, therefore, we introduce a relaxed notion of supervenience:
\begin{defi}
\label{def2}
Given $\varepsilon > 0$, $\mM$ is said to $\varepsilon$-\textit{supervene} on $\mB$ for distribution $F=F_{MB}$, denoted $\MeB$, if and only if $L_{F}(g^*) < \varepsilon$.
\end{defi}
\noindent Given this relaxation, consider the problem of testing for $\eps$-supervenience:
\begin{align*}
	H_0^{\eps}: L^* \geq \eps \\
	H_A^{\eps}: L^* < \eps
\end{align*}
Let $\mh{n}= n' \hL^{n'}_{F}(g_n)$ be the test statistic.  The distribution of $\mh{n}$ is available under the least favorable null distribution to the alternate hypothesis.  For the above hypothesis test,  the $p$-value is given by the binomial cumulative distribution function, $\mathbb{B}(\mh{n}; n', \eps)= \sum_{k \in [\mh{n}]_0}$Binomial$(k; n'; \eps)$, where $[\mh{n}]_0=\{0,1,\ldots, \mh{n}\}$.  We therefore reject whenever this $p$-value is less than $\alpha$; rejection implies that we are $100(1-\alpha$)\% confident that $\MeB$.

A test is \emph{consistent} whenever its power  (the probability of a rejecting the null when it is indeed false)  goes to unity as $n$ increases. For any statistical test, if the $p$-value converges in distribution to $\delta_0$ (point mass at zero), then whenever $\alpha >0$, power goes to unity.  For the above $\eps$-supervenience statistical test, if $g_n \conv g^*$ as $n \conv \infty$, then $\hL^{n'}_F(g_n) \conv L^*$ as $n,n' \conv \infty$.  Thus, if $L^* < \eps$, the $p$-value converges; that is, $\mathbb{B}(\mh{n}; n', \eps) \conv \delta_0$.

The definition of $\eps$-supervenience therefore admits, for the first time to our knowledge, a viable statistical test of supervenience, given a specified $\eps$ and $\alpha$. Moreover, this test is consistent whenever $g_n$ converges to the Bayes classifier, $g^*$.

Unfortunately, the rate of convergence of $L_{F}(g_n)$ to $L_{F}(g^*)$ depends on the (unknown) distribution $F=F_{MB}$ \cite{DGL96}. Furthermore, arbitrarily slow convergence theorems regarding the rate of convergence of $L_{F}(g_n)$ to $L_{F}(g^*)$ demonstrate that there is no universal $n,n'$ which will guarantee that the test has power greater than any specified target $\beta > \alpha$ \cite{Devroye83}. For this reason, the test outlined above can provide only a one-sided conclusion: if we reject we can be $100(1-\alpha)$\% confident that $\MeB$ holds, but we can never be confident in its negation; rather, it may be the case that the evidence in favor of $\MeB$ is insufficient for any number of reasons, including that we simply have not yet collected enough data. Thus, without restrictions on $F_{MB}$, arbitrarily slow convergence theorems imply that our theorem of $\varepsilon$-supervenience does not \tr{strictly} satisfy Popper's {\it falsifiability} requirement \cite{Popper}.

\subsection*{The availability of a consistent statistical test for supervenience} % (fold)
\label{sub:uc}

The above considerations indicate the existence of a consistent test for supervenience whenever the classifier used is consistent.  
% that to construct a statistical test with guaranteed limiting unity power, a universally consistent classifier (one for which $\hL^{n'}_F(g_n) \conv L_F(g^*)$ as $n,n' \conv \infty$) is required. 
To actually implement such a test, one must be able to (i) measure mind/brain pairs and (ii) have a consistent classifier $g_n$.  Unfortunately, we do not know how to measure the entirety of one's brain, much less one's mind. Moreover, even if we did, we do not know the joint distribution of mind/brain pairs, $F_{MB}$.  We therefore must restrict our interest to a mental property/brain property pair.  
A mental property might be a person's intelligence, psychological state, current thought, gender identity, etc.  A brain property might be the number of cells in a person's brain at some time $t$, or the collection of spike trains of all neurons in the brain during some time period $t$ to $t'$.  Regardless of the details of the specifications of the mental property and the brain property, given such specifications, one can assume a model, $\mc{F}$.  We would like a classifier, $g_n$, that is guaranteed to be consistent, no matter which of the possible distributions $F_{MB} \in \mc{F}$ is the true distribution.  A classifier with such a property is called an \emph{universally consistent classifier}.  Below, we show that under a very general mind-brain model $\mc{F}$, an universally consistent classifier is readily available.

@@

\begin{thex}
Let the physical property under consideration be brain connectivity structure, so $b$ is a brain-graph (``connectome'') with vertices representing neurons (or collections thereof) and edges representing synapses (or collections thereof). Further let $\mB$, the brain observation space, be the collection of all graphs on a given finite number of vertices, and $\mc{M}$, the mental property observation space, be finite. Now, imagine collecting very large amounts of very accurate identically and independently sampled  brain-graph data and the associated mental property indicators from $F_{MB}$. A $k_n$-nearest neighbor classifier using a Frobenius norm is universally consistent (see Methods for details). Therefore, %Theorem \ref{thm1} applies and 
the existence of a universally consistent classifier guarantees that eventually (in $n,n'$) we will be able to conclude $\MeB$ for this mind-brain property pair, if indeed $\varepsilon$-supervenience holds. This logic holds for directed graphs or multigraphs or hypergraphs with discrete edge weights and vertex attributes, as well as unlabeled graphs (see \cite{VP11_unlabeled} for details). Furthermore, the proof holds for other matrix norms (which might speed up convergence), and the regression scenario, where $|\mM|$ is infinite (again, see Methods for details).  
\end{thex}

\subsection*{The feasibility of a consistent statistical test for supervenience} % (fold)

The above argument demonstrates the availability of a consistent test under certain restrictions.  The arbitrary slow convergence theorem, however, demonstrates that convergence rates might be unbearably slow.  We therefore provide a (hopefully illustrative) example of the feasibility of such a test on synthetic data.

@@

We consider $k_n$-nearest neighbor classification of labeled multigraphs (directed, with loops) on 279 vertices, under Frobenius norm. The $k_n$-nearest neighbor classifier used here satisfies $k_n \rightarrow \infty$ as $n \rightarrow \infty$ and $k_n/n \rightarrow 0$ as $n \rightarrow \infty$, ensuring universal consistency. (Better classifiers can be constructed for the joint distribution $F_{M,B}$ used here; however, we demand universal consistency.)  Figure \ref{fig1} shows that for this simulation, rejecting $\eps=0.1$-supervenience at $\alpha=0.01$ only requires a few hundred training samples.

% Simulations suggest that one may build a classifier, practically and with a manageable training sample size $n$, that demonstrates $\varepsilon$-supervenience with reasonable choices for $\varepsilon$ and $\alpha$, and a plausible joint distribution $F_{M,B}$ (Figure \ref{fig1}).

>>>>

\newtheorem{defi}{Definition}
\newtheorem{thm}{Theorem}
\newtheorem{thex}{\emph{Gedankenexperiment}}
\lhead{Vogelstein JT, et al.}
\rhead{Statistical Supervenience}

@@

\noindent Questions and assumptions about mind-brain supervenience go back at least as far as Plato's dialogues in circa 400 BCE \cite{Plato97}.  While there are many different notions of supervenience, we find Davidson's canonical description particularly illustrative \cite{Davidson70}:
%  The mind-brain supervenience notion was canonized in 1970 with the following quote from Donald Davidson \cite{Davidson70}:
\begin{quotation}
\noindent [mind-brain] supervenience might be taken to mean that there cannot be two events alike in all physical respects but differing in some mental respect, or that an object cannot alter in some mental respect without altering in some physical respect.
\end{quotation}
This philosophical conjecture has potentially widespread implications.  
% We consider a special case of supervenience of considerable interest.  Specifically, this work addresses a version of a local supervenience between mental properties and brain properties, with particular emphasize on brain-graphs (i.e., connectivity structure).  Supervenience questions or assumptions are fundamental to 
% The determination of supervenience (or lack thereof) of minds on brains has potentially important implications in 
% a number of fields of inquiry.  
For example, neural network theory and artificial intelligence often implicitly assume 
% take a generalized notion of 
a local version mind-brain supervenience 
% as an assumption 
% , which if falsified, might change modern approaches to learning 
\cite{Haykin2008,Ripley2008}. Cognitive neuroscience similarly seems to operate under such assumptions
% , which if falsified, might result in novel perspectives and theories 
\cite{Fodor1998, Gazzaniga2008}.  Philosophers continue to debate and refine notions of supervenience 
% And the question of mind-brain supervenience continues to be debated amongst philosophers 
\cite{Kim2007}.  
% Moreover, many cognitive neuroscience investigations could be cast as questions
Yet, to date, relatively scant attention has been paid to what might be empirically learned about supervenience.

In this work we attempt to bridge the gap between philosophical conjecture and empirical investigations by casting supervenience in a probabilistic framework amenable to hypothesis testing. 
We then use the probabilistic theory of pattern recognition to determine
 % This perspective leads to a greater understanding vis-\'a-vis 
the limits of what one can and cannot learn about supervenience through data analysis.

% This work does not attempt to resolve any particular mind-brain supervenience debates.  Rather, we propose a statistical approach for framing mind-brain supervenience questions.  This approach depends on defining the space of mental and brain properties under investigation and a statistical model characterizing the possible distributions governing their relationship.  Such definitions transform supervenience from a conjecture or an assumption into a hypothesis which can be tested.

@@

\noindent Let $\mc{M}=\{m_1, m_2, \ldots\}$ be the space of all possible minds and
let $\mc{B}=\{b_1,b_2,\ldots\}$ be the set of all possible brains.  $\mc{M}$ includes a mind for each possible collection of thoughts, memories, beliefs, etc.
$\mc{B}$ includes a brain for each possible position and momentum of all subatomic particles within the skull.  
Given these definitions, Davidson's conjecture may be concisely and formally stated thusly:  $m \neq m' \implies b \neq b'$, where $(m,b), (m',b') \in \mc{M} \times \mc{B}$ are mind-brain pairs.  This mind-brain supervenience relation does not imply an injective relation, a causal relation, or an identity relation (see Appendix 1 for more details and some examples).  To facilitate both statistical analysis and empirical investigation, we convert this supervenience relation from a logical to a probabilistic relation.

% Let $b$ correspond to an agent's brain, which is a particular element from the set of all possible brains, $\mB$. Similarly, let $m$ correspond to an agent's mind, which is a particular element from the set of all possible minds, $\mM$.  
Let $F_{MB}$ indicate a joint distribution of minds and brains. Statistical supervenience can then be defined as follows:
\begin{defi}
\label{def:1} 
$\mM$ is said to \textit{statistically supervene} on $\mB$ for distribution $F=F_{MB}$, denoted $\mM \overset{S}{\sim}_F \mB$, if and only if $\PP[m \neq m' | b=b']=0$, or equivalently $\PP[m = m' | b = b']=1$. 
\end{defi}
\noindent Statistical supervenience is therefore a probabilistic relation on sets (which could be considered a generalization of correlation; see Appendix 1 for details).

@@

% Given that 
If minds statistically supervene on brains, 
% , $\MsB$, 
then if two minds differ, there must be some brain-based difference to account for the mental difference.  This means that there must exist a deterministic function $g^*$ mapping each brain to its supervening mind. One could therefore, in principle, know this function. When the space of all possible minds is finite---that is, $|\mM| < \infty$---any function $g\from \mB \to \mM$ mapping from minds to brains is called a \emph{classifier}.  
% Let $\mh{m}$ denote the output of a classifier, $g(b)=\mh{m}$.  
Define misclassification rate, the probability that $g$ misclassifies $b$ under distribution $F=F_{MB}$,  as
\begin{align} \label{eq:1}
L_{F}(g) = \PP[g(B) \neq M] =  \sum_{(m,b) \in \mc{M} \times \mc{B}} \II\{g(b) \neq m\} \PP[B=b, M=m],	
\end{align}
where $\II\{\cdot\}$ denotes the indicator function taking value unity whenever its argument is true and zero otherwise.  The Bayes optimal classifier $g^*$ minimizes $L_{F}(g)$ over all classifiers:	
$g^* = \argmin_{g} L_{F}(g)$.
The \emph{Bayes error}, or Bayes risk, $L^*=L_{F}(g^*)$, is the minimum possible misclassification rate.

% The optimal such classifier, $g^*$, has the smallest expected misclassification rate, $L^*=L_{F}(g^*)$, under distribuion $F$.  The minimum misclassification rate is called Bayes error (see Methods for details). 
The primary result of casting supervenience in a statistical framework is the below theorem, which 
follows immediately from Definition \ref{def:1} and Eq. \eqref{eq:1}: 
\begin{thm}
\label{thm:1} 
% $\mM$ is said to \textit{statistically supervene} on $\mB$ for distribution $F=F_{MB}$, denoted 
$\mM \overset{S}{\sim}_{F} \mB \Leftrightarrow L^*= 0$.
 %Formally, \mbox{$\MsB \Leftrightarrow L^*=0$}.  
\end{thm}
% \begin{proof}
% Let $\mc{M}_b=\{m: \PP[B=b | M=m] >0\}$.  
% $$L^*=0 \Leftrightarrow |\mc{M}_b|=1 \, \forall \, b\in \mc{B} : \PP[B=b]>0. $$
% In words, for $L^*$ to equal 0, it must be the case that there exists only a single $m$ for each $b$.
% \end{proof}

@@

The above argument shows (for the first time to our knowledge) that statistical supervenience and zero Bayes error are equivalent. Statistical supervenience can therefore be thought of as a constraint on the possible distributions on minds and brains.  Specifically, let $\mc{F}$ indicate the set of all possible joint distributions on minds and brains, and let $\mc{F}_s = \{F_{MB} \in \mc{F}: L^*=0\}$ be the subset of distributions for which supervenience holds. Theorem \ref{thm:1} implies that $\mc{F}_s  \subsetneqq \mc{F}$.  Mind-brain supervenience is therefore an extremely restrictive assumption about the possible relationships between minds and brains.  It seems that such a restrictive assumption begs for empirical evaluation, vis-\'a-vis, for instance, a hypothesis test.

\subsection*{The non-existence of a viable statistical test for supervenience} % (fold)
\label{sub:subsection_name}

@@

The above theorem implies that if we desire to know whether  minds supervene on brains, we can check whether $L^*=0$.  Unfortunately, $L^*$ is typically unknown.  Fortunately, we can approximate $L^*$ using training data.

Assume that training data $\mc{T}_n=\{(M_{1},B_{1}), \ldots, (M_{n},B_{n})\}$ are each sampled identically and independently (iid) from the true (but unknown) joint distribution $F=F_{MB}$.  Let $g_n$ be a classifier induced by the training data, $g_n:\mB \times (\mc{M} \times \mc{B})^n \mapsto \mM$.  The  misclassification rate of such a classifier is given by
\begin{align}
L_F(g_n)=\sum_{(m,b)  \in \mc{M}\times \mc{B}} \II\{g_n(b; \mc{T}_n) \neq m\} \PP[B=b,M=m],
\end{align}
%  The expected misclassification rate is given by 
% \begin{align}
% \EE[L_F(g_n)]=\sum_{(m,b)  \in \mc{M}\times \mc{B}} \II\{g_n(b; \mc{T}_n) \neq m\} \PP[B=b,M=m],
% \end{align}
which is a random variable due to the dependence on a randomly sampled training set $\mc{T}_n$.  
% where the expectation is taken with respect to the training data $\mc{T}_n$. 
Calculating the expected misclassification rate $\EE[L_F(g_n)]$ is often intractable in practice because it requires a sum over all possible training sets.  Instead, expected misclassification rate can be approximated by ``hold-out'' error.  Let $\mc{H}_{n'}=\{(M_{n+1},B_{n+1}), \ldots, (M_{n+n'},B_{n+n'})\}$ be a set of $n'$ hold-out samples, each sampled iid from $F_{MB}$.  The hold-out approximation to the misclassification rate is given by
\begin{align}
\hL^{n'}_{F}(g_{n}) = \sum_{(M_i,B_i) \in \mc{H}_{n'}}\II \{g_{n}(B_i; \mc{T}_{n})\neq M_i\} \approx \EE[L_F(g_n)] \geq L^*. % \PP[B=b,M=m].	
\end{align}
% Under the above assumptions, $\hL^{n'}_F(g_n)$ 
% which can be used as a surrogate for $L^*$. 
By definition of $g^*$, the expectation of $\hL^{n'}_F(g_n)$ (with respect to both $\mc{T}_n$ and $\mc{H}_{n'}$)  is greater than or equal to $L^*$ for any $g_n$ and all $n$.  Thus, we can construct a hypothesis test for $L^*$ using the surrogate $\hL^{n'}_F(g_n)$.

A statistical test proceeds by 
specifying the allowable Type I error rate $\alpha>0$ and then
calculating a 
test statistic.
The $p$-value---the probability of rejecting the least favorable null hypothesis (the simple hypothesis within the potentially composite null which is closest to the boundary with the alternative hypothesis)---is the probability of observing a result at least as extreme as the observed.  In other words, the $p$-value is the cumulative distribution function of the test statistic evaluated at the observed test statistic with parameter given by the least favorable null distribution.
% a functional of the distribution of the test statistic.  
% and a critical value $c_\alpha$.  
We reject if 
% the test statistic is more extreme than the critical value, or equivalently, if 
the $p$-value 
is less than $\alpha$.   A test is \emph{consistent} whenever its power  (the probability of rejecting the null when it is indeed false)  goes to unity as $n\conv \infty$ . For any statistical test, if the $p$-value converges in distribution to $\delta_0$ (point mass at zero), then whenever $\alpha >0$, power goes to unity.

% Ideally, 
Based on the above considerations,
we might consider the following hypothesis test: $H_0: L^*>0$ and $H_A: L^*=0$; rejecting the null indicates that $\MsB$. Unfortunately, 
% because the null hypothesis is not closed, 
the alternative hypothesis lies on the boundary, so the $p$-value is always equal to unity \cite{Bickel2000}.  From this, Theorem \ref{thm:2} follows immediately:
\begin{thm} \label{thm:2}
	There does not exist a viable test of $\MsB$
\end{thm}

In other words, we can \emph{never} reject $L^*>0$ in favor of supervenience, no matter how much data we obtain.  Supervenience therefore does not satisfy Popper's falsifiability criterion \cite{Popper1959}.

\subsection*{The existence of a consistent statistical test for $\eps$-supervenience} % (fold)

To proceed, therefore, we introduce a relaxed notion of supervenience: 
% Let $\MeB$ denote that $\mc{M}$ is $\eps$-supervenient on $\mc{B}$ for distribution $F=F_{MB}$, for $\eps>0$.  We define $\MeB$ as follows:
\begin{defi}
\label{def:2}
$\mM$ is said to $\eps$-\textit{supervene} on $\mB$ for distribution $F=F_{MB}$, denoted $\MeB$, if and only if $L^*< \eps$ for some $\eps>0$.
% $$\MeB \Leftrightarrow L^*< \eps.$$
% Given $\varepsilon > 0$, $\mM$ is said to $\varepsilon$-\textit{supervene} on $\mB$ for distribution $F=F_{MB}$ if and only if $L_F(g^*)< \eps$. 
%, denoted $\MeB \Leftrightarrow L_{F}(g^*) < \varepsilon$.
\end{defi}
\noindent 
% For brevity, let $\MeB$ denote that $\mc{M}$ is $\eps$-supervenient on $\mc{B}$ 
Given this relaxation, consider the problem of testing for $\eps$-supervenience:
\begin{align*}
	H_0^{\eps}: L^* \geq \eps \\
	H_A^{\eps}: L^* < \eps.
\end{align*}
Let $\mh{n}= n' \hL^{n'}_{F}(g_n)$ be the \emph{test statistic}. 
The distribution of $\mh{n}$ is available under the least favorable null distribution. 
% to the alternative hypothesis.  
% The $p$-value is given by the least favorable null distribution to the alternative hypothesis.
For the above hypothesis test,  
% for this hypothesis test 
the $p$-value is therefore the binomial cumulative distribution function with parameter $\eps$; that is, $p$-value $=\mathbb{B}(\mh{n}; n', \eps)= \sum_{k \in [\mh{n}]_0}$Binomial$(k; n'; \eps)$, where
% Let 
% and
$[\mh{n}]_0=\{0,1,\ldots, \mh{n}\}$.  We reject whenever this $p$-value is less than $\alpha$; rejection implies that we are $100(1-\alpha$)\% confident that $\MeB$.

 For the above $\eps$-supervenience statistical test, if $g_n \conv g^*$ as $n \conv \infty$, then $\hL^{n'}_F(g_n) \conv L^*$ as $n,n' \conv \infty$.  Thus, if $L^* < \eps$, 
power goes to unity.
% the $p$-value converges; that is, $\mathbb{B}(\mh{n}; n', \eps) \conv \delta_0$.
The definition of $\eps$-supervenience therefore admits, for the first time to our knowledge, a viable statistical test of supervenience, given a specified $\eps$ and $\alpha$. Moreover, this test is consistent whenever $g_n$ converges to the Bayes classifier $g^*$.

Unfortunately, the rate of convergence of $L_{F}(g_n)$ to $L_{F}(g^*)$ depends on the (unknown) distribution $F=F_{MB}$ \cite{DGL96}. Furthermore, arbitrarily slow convergence theorems regarding the rate of convergence of $L_{F}(g_n)$ to $L_{F}(g^*)$ demonstrate that there is no universal $n,n'$ which will guarantee that the test has power greater than any specified target $\beta > \alpha$ \cite{Devroye83}. For this reason, the test outlined above can provide only a one-sided conclusion: if we reject we can be $100(1-\alpha)$\% confident that $\MeB$ holds, but we can never be confident in its negation; rather, it may be the case that the evidence in favor of $\MeB$ is insufficient 
% for any number of reasons, including that 
because we simply have not yet collected enough data. 
% Thus, without restrictions on $F_{MB}$, arbitrarily slow convergence theorems imply that our theorem of $\varepsilon$-supervenience does not \tr{strictly} satisfy Popper's {\it falsifiability} requirement \cite{Popper}.

\subsection*{The availability of a consistent statistical test for $\eps$-supervenience} % (fold)
\label{sub:uc}

The above considerations indicate the existence of a consistent test for $\eps$-supervenience whenever the classifier used is consistent.  
% that to construct a statistical test with guaranteed limiting unity power, a universally consistent classifier (one for which $\hL^{n'}_F(g_n) \conv L_F(g^*)$ as $n,n' \conv \infty$) is required. 
To actually implement such a test, one must be able to (i) measure mind/brain pairs and (ii) have a consistent classifier $g_n$.  Unfortunately, we do not know how to measure the entirety of one's brain, much less one's mind. 
% Moreover, even if we did, we do not know the joint distribution of mind/brain pairs, $F_{MB}$.  
We therefore must restrict our interest to a mind/brain \emph{property} pair.  
A mind (mental) property might be a person's intelligence, psychological state, current thought, gender identity, etc.  A brain property might be the number of cells in a person's brain at some time $t$, or the collection of spike trains of all neurons in the brain during some time period $t$ to $t'$.  Regardless of the details of the specifications of the mental property and the brain property, given such specifications, one can assume a model, $\mc{F}$.  We would like a classifier, $g_n$, that is guaranteed to be consistent, no matter which of the possible distributions $F_{MB} \in \mc{F}$ is the true distribution.  A classifier with such a property is called a \emph{universally consistent classifier}.  
Below, under a very general mind-brain model $\mc{F}$, we construct a universally consistent classifier. 
% is readily available.

@@

\begin{thex} \label{exp:1}
Let the physical property under consideration be brain connectivity structure, so $b$ is a brain-graph (``connectome'') with vertices representing neurons (or collections thereof) and edges representing synapses (or collections thereof). Further let $\mB$, the brain observation space, be the collection of all graphs on a given finite number of vertices, and let $\mc{M}$, the mental property observation space, be finite. Now, imagine collecting very large amounts of very accurate identically and independently sampled  brain-graph data and associated mental property indicators from $F_{MB}$. A $k_n$-nearest neighbor classifier using a Frobenius norm is universally consistent (see Methods for details). 
% Therefore, %Theorem \ref{thm:1} applies and 
The existence of a universally consistent classifier guarantees that eventually (in $n,n'$) we will be able to conclude $\MeB$ for this mind-brain property pair, if indeed $\varepsilon$-supervenience holds. This logic holds for directed graphs or multigraphs or hypergraphs with discrete edge weights and vertex attributes, as well as unlabeled graphs (see \cite{VP11_unlabeled} for details). Furthermore, the proof holds for other matrix norms (which might speed up convergence and hence reduce the required $n$), and the regression scenario where $|\mM|$ is infinite (again, see Methods for details).  
\end{thex}
Thus, under the conditions stated in the above \emph{Gedankenexperiment}, we have:
\begin{thm} \label{thm:3}
	$\MeB \implies \beta \conv 1$ as $n,n'\conv \infty$, but there is no universal $n,n'$ that guarantes $\beta=1$.
\end{thm}

\subsection*{The feasibility of a consistent statistical test for $\eps$-supervenience} % (fold)

Theorem \ref{thm:3} demonstrates the availability of a consistent test under certain restrictions.  The arbitrary slow convergence theorem, however, demonstrates that convergence rates might be unbearably slow.  We therefore provide an illustrative example of the feasibility of such a test on synthetic data.

@@

We consider $k_n$-nearest neighbor classification of labeled multigraphs (directed, with loops) on 279 vertices, under Frobenius norm. The $k_n$-nearest neighbor classifier used here satisfies $k_n \rightarrow \infty$ as $n \rightarrow \infty$ and $k_n/n \rightarrow 0$ as $n \rightarrow \infty$, ensuring universal consistency. (Better classifiers can be constructed for the joint distribution $F_{MB}$ used here; however, we demand universal consistency.)  Figure \ref{fig:1} shows that for this simulation, rejecting $(\eps=0.1)$-supervenience at $\alpha=0.01$ only requires a few hundred training samples.

% Simulations suggest that one may build a classifier, practically and with a manageable training sample size $n$, that demonstrates $\varepsilon$-supervenience with reasonable choices for $\varepsilon$ and $\alpha$, and a plausible joint distribution $F_{MB}$ (Figure \ref{fig:1}).
